---
title: "Project 1/2 - Statistic Inference"
author: "ctakamiya"
date: "September 14, 2014"
output: pdf_document
---

#1 - Loading the ToothGrowth data and performing some basic exploratory data analyses 

```{r}
data (ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)
tail(ToothGrowth)
```

#2 - A basic summary of the data.
Average of length by type supplementar
```{r}
summary(ToothGrowth[ToothGrowth$supp=="OJ",]$len)
summary(ToothGrowth[ToothGrowth$supp=="VC",]$len)
```

#3 - Using confidence intervals and hypothesis tests to compare tooth growth by supp and dose.
After initial exploratory data analysis, this data provide an intuition about 
the difference between OJ and VC averages in length. In another words, 
${\mu}_{OJ}  > {\mu}_{VC}$ or ${\mu}_{OJ}  - {\mu}_{VC} > 0$.
This test is not paired data, because the observations are independent.

$H_0: {\mu}_{OJ}  - {\mu}_{VC} = 0$ - There is no difference in length averages.

$H_A: {\mu}_{OJ}  - {\mu}_{VC} \neq 0$ - There is a difference in length averages.

```{r}
t.test(ToothGrowth[ToothGrowth$supp=="OJ",]$len, 
       ToothGrowth[ToothGrowth$supp=="VC",]$len,
       var.equal = FALSE)
```
# 4 Conclusions
The result in part 3 shows that there is no difference in length averages. Using
Confidence Interval (95%) we can verify that 0 (zero) is in the interval. Or by
significance ${\alpha} = 0.05$ and p-value > 0.05 (p-value=0.06063), we fail to 
reject $H_0$.
In another word, this data do not provide convincing evidence that OJ promotes 
more growth of  tooth length.

# Appendix
```{r fig.width=6, fig.height=4}
library(ggplot2)
qplot(len, data = ToothGrowth, facets=~supp, binwidth=3)
```


```{r fig.width=6, fig.height=4}
library(graphics)
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
       xlab = "ToothGrowth data: length vs dose, given type of supplement")
```