---
title: "Project 1/1 - Statistic Inference"
author: "ctakamiya"
date: "September 14, 2014"
output: pdf_document
---
# 1 Simulation exercises

In this part of Project the Exponential Distribution is simulated.
The exponential distribution mean is $1 / {\lambda}$ and the standard 
deviation is also $1 / {\lambda}$. The simultation make use of 
rexp(n, lambda) function that generates a random exponential distribution with 
rate lambda (i.e, mean = 1/lambda). 
Instructions for this project specifies ${\lambda}$ = 0.2 parameter
to simulation. 
The simulation do a 1000 simultated averages of 40 exponential(0.2)s. 
```{r}
n <- 40
nosim <- 1000
lambda <- 0.2
meansExp <- rowSums(matrix(rexp(n*nosim, rate=lambda), nosim)) / n
meanDist <- mean(meansExp)
meanDist
```
1 - This distribution is centered at: `r meanDist`. 
Theoretical center of this distribution is around the population mean,
E[$\bar{X}$] = $\mu$ = $1 / {\lambda}$ = $\frac{1}{`r lambda`}$ = `r 1/lambda`,

2 - The standard deviation (${\sigma}$) of exponential distribution is $\frac{1}{\lambda}$. Where 
${\lambda}=0.2$.
```{r}
sigma = 1 / 0.2
sigma
```
So we can conclude that the variation is ${\sigma}^2 =$ `r sigma ^ 2 `. 
The theoritical value of variation of distribution means is 
$\frac{{\sigma} ^ 2}{n}$. The logical estimation
is $\frac{S^2}{n} =\frac{`r sigma ^ 2`}{`r n`} = `r (sigma ^ 2 ) / n` $.
By simulation we can confirm this value is very close to variance.
```{r}
var(meansExp)
```

3 - The normal curve drawn below shows that the distribution is approximately 
normal.

```{r fig.width=5, fig.height=3}
library(ggplot2)
df <- data.frame(meansExp)
ggplot(df, aes(x=df$meansExp)) + 
     geom_histogram(aes(y=..density..),     
                    binwidth=.5,
                    colour="black", fill="white") +
        stat_function(fun = dnorm, colour = "red", 
                      arg = list(mean=5, sd=sigma/sqrt(n))) +
        labs(x= "x")
```

4 - The interval confidence $\bar{X} \pm 1.96 \frac{S}{\sqrt(n)}$ is called 95%
interval for ${\mu}$ and the interval is [`r meanDist - 1.96 * sd(meansExp) / sqrt(n)`, 
`r meanDist + 1.96 * sd(meansExp) / sqrt(n)` ]. This represents that about 95% 
of intervals obtained would contain ${\mu}$.




